An ultra-low noise, high-voltage piezo driver

### 2015-12-23 piezo.tex
Added mostly completed schematic; beginning of description of circuit

\usepackage{siunitx}
\usepackage{amsmath}

@@

\begin{figure}[ht]
\includegraphics[width=\linewidth]{fig/PiezoCircuit.ai}
%\captionsetup{justification=justified}
\caption{Schematic of the high voltage stabilization.
The voltage HV is generated using a Texas Instruments DRV2700 high voltage driver in flyback configuration (see Fig.~\ref{Fig:DRV2700}).
A fast, very high slew-rate op-amp senses the output voltage across $R_1$ and $R_2$, and servos it by modulating the node at ``HV floating gnd''.
The $V_{\text{DC}}$ gain is set by $\left(1+R_1/R_2\right)$, while the modulation gain is set by $-R_{\text{mod}}/R_{\text{fb}}$.
The capacitor linking the floating ground node to the output allows the op-amp to remove residual switching noise and stabilize the DC output according to the transfer function given in Eq.~(\ref{Eq:PiezoTransfer}). \label{Fig:PiezoCircuit}}
\end{figure}

Discussion of individual circuit components

>>>>

\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{amsfonts}

@@

The core elements of this circuit revolve around the newly-available Texas Instruments DRV2700 piezo driver.
\footnote{The identification of commercial products is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}
This single-chip integrated circuit can be operated as a boost converter driving an on-chip differential amplifier up to \SI{100}{\volt}, or as a flyback regulator up to \SI{1}{\kilo\volt}. 
In flyback configuration, the DRV2700 drives a step-up transformer, providing the galvanically isolated voltage $\mathbf{HV}$ at its output; see Fig.~\ref{Fig:DRV2700}.

\begin{figure*}[t]
\includegraphics[width=\textwidth]{fig/DRV2700.ai}
\caption{Schematic of the high voltage stabilization.
The voltage HV is generated using a Texas Instruments DRV2700 high voltage driver in flyback configuration (see Fig.~\ref{Fig:DRV2700}).
A fast, very high slew-rate op-amp senses the output voltage across $R_1$ and $R_2$, and servos it by modulating the node at ``HV floating gnd''.
The $V_{\text{DC}}$ gain is set by $\left(1+R_1/R_2\right)$, while the modulation gain is set by $-R_{\text{mod}}/R_{\text{fb}}$.
The capacitor linking the floating ground node to the output allows the op-amp to remove residual switching noise and stabilize the DC output according to the transfer function given in Eq.~(\ref{Eq:PiezoTransfer}). \label{Fig:PiezoCircuit}}
\end{figure*}

In isolation, the DRV2700 is not suited for low-noise laboratory instrumentation. 
The output ripple, even after heavy filtering, can be as high as a few volts, and standard filter techniques to reduce this noise simultaneously reduce the modulation bandwidth.
Even if this were not the case, it remains unlikely that the RMS noise could be brought below $\SI{1}{\milli\volt}$, which is the regime we would like to operate in for certain low-noise applications in the laboratory.
With this in mind, we designed a circuit that leverages the integrated flyback regulator of the DRV2700 but uses a secondary feedback mechanism to both eliminate switching noise and provide a low-gain, DC-coupled feedback path for closed loop applications.
